---
title: "Coursera project"
author: "Diego Marty"
date: "20/05/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
```{r}
library(caret);library(doParallel);library(randomForest)
set.seed(23454561)


#we read the training and test sets#
#we replace any blank or undifined value by 'NA'#
```{r}
trainingSet <- read.csv('pml-training.csv', na.strings=c("NA","#DIV/0!", ""))
testSet <- read.csv('pml-test.csv' , na.strings=c("NA", "#DIV/0!", ""))
```

#We decide to keep only columns that at least half full#
#Other variables are not taken into account#
```{r}
keptVariables    <- which((colSums(!is.na(trainingSet)) >= 0.5*nrow(trainingSet)))
trainingSet <- trainingSet[,keptVariables]
testSet <- testSet[,keptVariables]
```

#We fix issues about variables ID and factor levels#
```{r}
testSet <- testSet[-ncol(testSet)]
testSet$new_window <- factor(testSet$new_window, levels=c("no","yes"))
```

#We also remove the X and the timestamp variables as they are useless#
```{r}
trainingSet <- trainingSet[,-c(1,5)]
testSet <- testSet[,-c(1,5)]
```

#Now we can partition the data into 60% training set and 40% test set#
```{r}
training <- createDataPartition(trainingSet$classe, p = 0.6, list = FALSE)
training <- trainingSet[training, ]
testing <- trainingSet[-training, ]
```

#We put 
```{r}
class <- training$classe
data <- training[-ncol(training)]
```

#fitting random forests model#
```{r}
registerDoParallel()
rf <- train(data, class, method="parRF", 
            tuneGrid=data.frame(mtry=3), 
            trControl=trainControl(method="none"))
```

#computing the confusion Matrix for the testing set#
```{r}
testingPredictions <- predict(rf, newdata=testing)
confMatrix <- confusionMatrix(testingPredictions,testing$classe)
confMatrix
confMa```trix$overall[1]
```

#submitting results#
```{r}
pml_write_files = function(x){
  n = length(x)
  for(i in 1:n){
    filename = paste0("problem_id_",i,".txt")
    write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
  }
}

answers <- predict(rf, testSet)
pml_write_files(answers)
```
